A mechanical Model of Rod-Shaped Bacteria

### 2025-01-29 paper/main.tex
insert as individual figure later
add section for parameter estimation and profiles of parameters

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]
        {../docs/source/_static/fitting-methods/penalty-time-flow.png}%
    \includegraphics[width=0.5\textwidth]
        {../docs/source/_static/fitting-methods/displacement-calculations.png}
    \caption{Comparison of masks across generations. Compare estimated with exact rod lengths.}
    \label{fig:benchmarking-fitting-algorithm}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.32\textwidth]
        {../docs/source/_static/fitting-methods/estimate-parameters1/Growth Rate.png}%
    \includegraphics[width=0.32\textwidth]
        {../docs/source/_static/fitting-methods/estimate-parameters1/Potential Stiffness.png}%
    \includegraphics[width=0.32\textwidth]
        {../docs/source/_static/fitting-methods/estimate-parameters1/Radius.png}\\%
    \includegraphics[width=0.32\textwidth]
        {../docs/source/_static/fitting-methods/estimate-parameters1/Rigidity.png}%
    \includegraphics[width=0.32\textwidth]
        {../docs/source/_static/fitting-methods/estimate-parameters1/Strength.png}%
    \caption{Snapshots at \dots}
    \label{fig:parameter-estimates-single-step}
\end{figure}

@@

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]
        {../docs/source/_static/fitting-methods/displacement-calculations.png}
    \caption{Comparison of masks across generations. Compare estimated with exact rod lengths.}
    \label{fig:benchmarking-fitting-algorithm}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.33\textwidth]
        {../docs/source/_static/fitting-methods/estimate-parameters1/microscopic-images-0.png}%
    \includegraphics[width=0.33\textwidth]
        {../docs/source/_static/fitting-methods/estimate-parameters1/microscopic-images-1.png}%
    \includegraphics[width=0.33\textwidth]
        {../docs/source/_static/fitting-methods/estimate-parameters1/Growth Rate.png}\\%
    \includegraphics[width=0.33\textwidth]
        {../docs/source/_static/fitting-methods/estimate-parameters1/microscopic-images-2.png}%
    \includegraphics[width=0.33\textwidth]
        {../docs/source/_static/fitting-methods/estimate-parameters1/microscopic-images-3.png}%
    \includegraphics[width=0.33\textwidth]
        {../docs/source/_static/fitting-methods/estimate-parameters1/Potential Stiffness.png}\\
    \includegraphics[width=0.33\textwidth]
        {../docs/source/_static/fitting-methods/estimate-parameters1/Radius.png}%
    \includegraphics[width=0.33\textwidth]
        {../docs/source/_static/fitting-methods/estimate-parameters1/Rigidity.png}%
    \includegraphics[width=0.33\textwidth]
        {../docs/source/_static/fitting-methods/estimate-parameters1/Strength.png}%
    \caption{Profiles of the Parameters}
    \label{fig:parameter-estimates-single-step}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]
        {../docs/source/_static/fitting-methods/penalty-time-flow.png}%
    \caption{Comparison of masks across generations.}
    \label{fig:penalty-calculation-cell-division}
\end{figure}
